Upper limits on CN from exocomets transiting $\beta$~Pictoris

### 2025-04-11 src/tex/ms.tex
removed bolding

From the multiple detections of exocomets in spectroscopy towards \bp{}, the broadband detection of exocomet tails transiting a star were predicted in \citet{1999A&A...343..916L}.
%
{\bf A chain of seven exocomets were proposed to explain the shape of one eclipse seen towards KIC~8462852 in \citet{Kiefer17}, and
single exocomet transits were subsequently detected towards the star KIC~3542116 \citep{Rappaport18} with the {\it Kepler} satellite \citep{Borucki10} and in TESS data towards \bp{} \citep{Zieba19}.}
%
Observations of \bp{} in subsequent TESS sectors revealed over two dozen transits whose depth follows a power law distribution similar to those of the Solar system \citep{LecavelierdesEtangs22,Pavlenko22}.
%
Automated searches in photometry \citep{Kennedy19} and spectroscopy \citep{BendahanWest24} for additional exocomet systems have been met with limited success.

@@

The night of 2018-05-06, which has a high signal-to-noise ratio, was chosen to act as an initial estimate for the blaze function.%(the night of 2018-05-06 and \hl{DATE} for UVES).
%
The individual spectra from this night were averaged together to further boost the signal-to-noise ratio.
%
Subsequently, each individual spectrum was divided by this reference spectrum to highlight the changes in the effective profile.
%
This ratio spectrum was subsequently binned using a bin-width of 81 pixels using a robust algorithm to remove outliers within each bin. This binned ratio was then fitted using a second order polynomial.
%
The original spectrum was finally divided by this polynomial to correct for the changes.

@@

%For both HARPS and UVES w
We first perform a second iteration of blaze corrections using a stellar spectrum constructed by averaging the spectra from periods with a low comet activity (see Sect.~\ref{sect:FEBid}).
%
%For HARPS
This is done separately pre- and post-fiber change. The correction is done similar to Sect.~\ref{sect:blaze}, however, an 8th order polynomial was used.

@@

\begin{figure}
    \begin{centering}
        \includegraphics[width=\columnwidth]{figures/spec_stack_CN_comet.pdf}
        \caption{Plot of the stacked spectrum in the comet rest frame (blue) with a CN model for $T=$300K and N=10$^{14}$\,cm$^{-2}$ overplotted in orange. The large signal around 3860\AA{} is due to the residual from a circumstellar \ion{Fe}{I} line.}
        \label{fig:spec_CN_comet_frame}
        \script{plot_spec_mean.py}
    \end{centering}
\end{figure}

@@

@@

The lifetime of \ce{HCN} for photodissociation into \ce{H}+\ce{CN} at 1~au has been calculated to be $(3.2-7.7)\times10^4$ sec, with lifetime of \ce{CN} dissociating into \ce{C}+\ce{N} being $(1.3-3.1)\times10^5$ sec \citep{Huebner92}, depending on solar activity levels.
%
These are consistent with the measured scale lengths above if the parents of \ce{CN} are ejected at $\sim 0.5$ \kms{}, and {\bf 
we take into account the excess photodissociation energy giving \ce{CN} an extra kick of $\simeq0.9$ \kms{} \citep{Fray2005}. 
}
\subsection{1P/Halley at \texorpdfstring{\bp{}}{Beta Pictoris}}

Photodissociation is  driven by the UV photon flux at the comet, which in turn is dominated by {\bf the Ly-$\alpha$ line flux \citep{Combi80}.
%
The  Ly-$\alpha$ emission from \bp{} has been measured by \citet{Wilson17} via HST+COS. Using their ISM and CSM corrected Voigt line profile parameters, we integrated over $\pm600$ \kms{} and corrected for the distance of \bp{} to derive an intrinsic Ly-$\alpha$ luminosity of $1.4\times10^{30}$ ergs sec$^{-1}$.

The solar Ly-$\alpha$  flux varies by $\sim 50\% $ over the Solar cycle, with a mean value at Earth of $4.7\times10^{11}$ phot s$^{-1}$ cm$^{-2}$ \citep{Woods00}. The resulting mean solar Ly-$\alpha$ luminosity is $2.1\times10^{28}$ ergs sec$^{-1}$, a factor of $\sim 67$ lower than \bp{}.
%From Ly-$\alpha$ measurements in \citet{Landsman93} the intrinsic Ly-$\alpha$ luminosity of A6V/A7V stars is a factor of $\sim10$ higher than for G2V stars.
%
Hence the photodissociation lifetime of \ce{CN}  at 1 au from \bp{} of an `exoHalley' will be approximately 67 times shorter i.e. $\sim 3000$ sec.
}

@@

$$n\sim\frac{3\times10^{31}}{\pi\cdot 1.7\times10^{22}}\sim 6\times10^{8}\:{\rm cm^{-2}}$$
Therefore an exoHalley at 1~au from \bp{} would result in a \ce{CN} column density of $10^{8}-10^{9}$ cm$^{-2}$.
%
This is 
{\bf
$\geq100$ times smaller than our measured upper limits above.
}
\subsection{Raising the \texorpdfstring{\ce{CN}}{CN} production rates}

@@

In summary, mechanisms exist by which the \ce{CN} column density of an exocomet at \bp{} 
{\bf
could exceed $10^{9}$ cm$^{-2}$.
%
A larger and/or hyperactive nucleus could increase $n$ by a factor of ten.
%
Even larger increases are possible with an outburst or comet disruption, but the upper boundary is likely to be near $n\sim10^{11}$ cm$^{-2}$. 
}

>>>>

From the multiple detections of exocomets in spectroscopy towards \bp{}, the broadband detection of exocomet tails transiting a star were predicted in \citet{1999A&A...343..916L}.
%
A chain of seven exocomets were proposed to explain the shape of one eclipse seen towards KIC~8462852 in \citet{Kiefer17}, and
single exocomet transits were subsequently detected towards the star KIC~3542116 \citep{Rappaport18} with the {\it Kepler} satellite \citep{Borucki10} and in TESS data towards \bp{} \citep{Zieba19}.
%
Observations of \bp{} in subsequent TESS sectors revealed over two dozen transits whose depth follows a power law distribution similar to those of the Solar system \citep{LecavelierdesEtangs22,Pavlenko22}.
%
Automated searches in photometry \citep{Kennedy19} and spectroscopy \citep{BendahanWest24} for additional exocomet systems have been met with limited success.

@@

The night of 2018-05-06, which has a high signal-to-noise ratio, was chosen to act as an initial estimate for the blaze function.%(the night of 2018-05-06 and \hl{DATE} for UVES).
%
The individual spectra from this night were averaged together to further boost the signal-to-noise ratio.
%
Subsequently, each individual spectrum was divided by this reference spectrum to highlight the changes in the effective profile.
%
This ratio spectrum was subsequently binned using a bin-width of 81 pixels using a robust algorithm to remove outliers within each bin, clipping points more than 2.7 Median Absolute Deviations (MAD) away from the median of each bin.
%
This binned ratio was then fitted using a second order polynomial.
%
The original spectrum was finally divided by this polynomial to correct for the changes.

@@

%For both HARPS and UVES w
We first perform a second iteration of blaze corrections using a stellar spectrum constructed by averaging the spectra from periods with a low comet activity (see Sect.~\ref{sect:FEBid}), similar to the method before, however, now using a wider binsize of 150 pixels and clipping outliers at 4.5 MAD away from the median.
%
%For HARPS
This is done separately pre- and post-fiber change. The correction is done similar to Sect.~\ref{sect:blaze}, however, an 8th order polynomial was used.

@@

\begin{figure}
    \begin{centering}
        \includegraphics[width=\columnwidth]{figures/spec_stack_CN_comet.pdf}
        \caption{Similar to Figure~\ref{fig:spec_CN_stellar_frame} but spectra are stacked in the rest frame of the comet. The large signal around 3860\AA{} is due to the residual from a circumstellar \ion{Fe}{I} line.}
        \label{fig:spec_CN_comet_frame}
        \script{plot_spec_mean.py}
    \end{centering}
\end{figure}

@@

When creating the CCFs, the region around the narrow, circumstellar \ion{Fe}{I} lines in this wavelength region (see Figs.~\ref{fig:spec_CN_stellar_frame}~and~\ref{fig:spec_CN_comet_frame}) were masked to avoid contamination, especially for the higher temperature CN models.
%
We masked the lines detected in \citep{Kiefer2018}, using a width of $\pm$0.35~$\AA$ for the \ion{Fe}{I} 3859.9$\AA$ line, while for the other lines a width of $\pm$0.15$\AA$ was used.

@@

The lifetime of \ce{HCN} for photodissociation into \ce{H}+\ce{CN} at 1~au has been calculated to be $(3.2-7.7)\times10^4$ sec, with lifetime of \ce{CN} dissociating into \ce{C}+\ce{N} being $(1.3-3.1)\times10^5$ sec \citep{Huebner92}, depending on solar activity levels.
%
These are consistent with the measured scale lengths above if the parents of \ce{CN} are ejected at $\sim 0.5$ \kms{}, and we take into account the excess photodissociation energy giving \ce{CN} an extra kick of $\simeq0.9$ \kms{} \citep{Fray2005}.

\subsection{1P/Halley at \texorpdfstring{\bp{}}{Beta Pictoris}}

Photodissociation is  driven by the UV photon flux at the comet, which in turn is dominated by the Ly-$\alpha$ line flux \citep{Combi80}.
%
The  Ly-$\alpha$ emission from \bp{} has been measured by \citet{Wilson17} via HST+COS.
%
Using their ISM and CSM corrected Voigt line profile parameters, we integrated over $\pm600$ \kms{} and corrected for the distance of \bp{} to derive an intrinsic Ly-$\alpha$ luminosity of $1.4\times10^{30}$ ergs sec$^{-1}$.

The solar Ly-$\alpha$ flux varies by $\sim 50\% $ over the Solar cycle, with a mean value at Earth of $4.7\times10^{11}$ phot s$^{-1}$ cm$^{-2}$ \citep{Woods00}.
%
The resulting mean solar Ly-$\alpha$ luminosity is $2.1\times10^{28}$ ergs sec$^{-1}$, a factor of $\sim 67$ lower than \bp{}.
%
Hence the photodissociation lifetime of \ce{CN} at 1 au from \bp{} of an `exoHalley' will be approximately 67 times shorter i.e. $\sim 3000$ sec.

@@

$$n\sim\frac{3\times10^{31}}{\pi\cdot 1.7\times10^{22}}\sim 6\times10^{8}\:{\rm cm^{-2}}$$
Therefore an exoHalley at 1~au from \bp{} would result in a \ce{CN} column density of $10^{8}-10^{9}$ cm$^{-2}$.
%
This is $\geq100$ times smaller than our measured upper limits above.

\subsection{Raising the \texorpdfstring{\ce{CN}}{CN} production rates}

@@

In summary, mechanisms exist by which the \ce{CN} column density of an exocomet at \bp{} could exceed $10^{9}$ cm$^{-2}$.
%
A larger and/or hyperactive nucleus could increase $n$ by a factor of ten.
%
Even larger increases are possible with an outburst or comet disruption, but the upper boundary is likely to be near $n\sim10^{11}$ cm$^{-2}$.
